A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-04-30 report_clean/abstract.tex
small issues
p.1 -> we focus on
+2 remarks taken into account
abstract: fixed

Hybrid resonance is a physical phenomenon
that appears for example in the heating of plasma,
and as such is of scientific interest in the development  of  the ITER project.
In this paper we focus some solutions with low regularity of Maxwell equations in
plasmas under strong background magnetic field.
Our purpose is two-fold.
On one hand we investigate the finite element approximation of the one dimensional problem 
written in the frequency domain, and on the other hand we investigate two different 
finite difference approximations of the one dimensional time dependent problem.
We will also compare the results of these different methods.

>>>>

Hybrid resonance is a physical phenomenon
that appears for example in the heating of plasma,
and as such is of scientific interest for the development  of  the ITER project.
In this paper \urev{we focus on} solutions of low regularity to Maxwell equations in
\mrev{magnetized plasmas}. 
Our main purpose is two-fold. First, we aim at the investigation of the finite element approximation 
of the frequency-domain problem. Second, we would like to study the resonant solutions 
in the time domain, with the help of two different finite difference approximations, 
and compare the results with the ones obtained in the frequency domain. This is done by  
numerical examination of the limiting absorption and limited amplitude principles.
